---
title: "Sorting Problem"
output: html_notebook
---
TESTING FIRST GIT COMMIT

Problem: Create an algorithm to check if an array of natural numbers is sorted in either ascending or decending order.


AscendingFunction (array)
  For {each} in {array}:
    If {each} - {next item} <= 0
    Return 

DescendingFunction (array)
  For {each} in {array}
    If {each} - {next item} => 0
    
First, I need to figure out how to reference the next item in the sequence
```{r}
##Testing for loop for referencing {next item}

seq <- c(2, 104, 6, 9)
print (seq[1+1]) #moves me up in the array
print(seq[1] + seq[2]) #Combines two objects in the array 

list <- (1:100)
for (i in list){
  if (list[i] < list[101]){
    print (i)
  }
}
```

Now we're putting together the ascending loop
    
```{r}
##Defining the array
nsorted <- c(5, 6, 7, 9, 2, 10, 14, 19, 20)
ysorted <- c(5, 6, 7, 8, 11, 14, 19, 20, 40)

arr <- ysorted

##ASCENDING
##Loop check if each value, when subtracted from itself+1 is still greater than or equal zero

notch <- 0
for (i in arr){
  if (notch < length(arr)){
    if (arr[i] < arr[i+1]){
      print ("Good")
      notch <- notch + 1
    }else {
      print ("Bad")
      notch <- notch + 1
    }
  }
}
```

Still having problems with the above script, which is the goal. But maybe creating it with a while loop would be more efficient

```{r}
##Trying again with while loop instead of For loop.

counter <- 0 
while (counter < length(arr)) {
  for (i in arr){
    if (arr[i] < arr[i+1]){
      print ("Good")
      counter <- counter + 1
      print (counter)
    }else {
      print ("Bad")
      counter <- length(arr)
    }
  }
}
```

